# Peer Assessement

## This is where the enthusiastic student I am starts ro learn R markdown.final version


First bit of code changes the options so that the code will always be available 
in the markdown document.

```{r setOptions, echo=TRUE}
library(markdown)
library(knitr)
opts_chunk$set(echo = TRUE)
```

###1. Code for reading in the dataset and/or processing the data

```{r}
actiData<- read.csv("activity.csv")
actiData$date<- as.Date(actiData$date, "%Y-%m-%d ")
```

###2. Histogram of the total number of steps taken each day
```{r}
library(ggplot2)
graph1<- ggplot(actiData, aes(date, steps, ))
graph1+ geom_bar(stat = "identity", na.rm = TRUE, fill = "dodgerblue4")

```

###3.Mean and median number of steps taken each day

```{r}
library(dplyr)
actiDataDay<- group_by(actiData,date)
results <-summarise(actiDataDay, meanS = mean(steps, na.rm = TRUE), medianS = median(steps, na.rm = TRUE) )
print(results, n = 20)
maxMean<- which.max(results$meanS)
maxMedian<- which.max(results$medianS)
maxMean
maxMedian
```
The maximum mean is `maxMean`. Du to a lot of "0", most medians are "0" and the biggest median is `maxMedian`



### 4.Time series plot of the average number of steps taken

```{r}
plot(results$date, results$meanS, col= "red")

```

###3.The 5-minute interval that, on average, contains the maximum number of steps
```{r}
actiDataInterval<- group_by(actiData, interval)
actiDataInterval<- summarise(actiDataInterval, meansteps =mean(steps, na.rm = TRUE))
# That interval is interval found on line :
which.max(actiDataInterval$meansteps)


```
###6.Code to describe and show a strategy for imputing missing data

```{r}
#Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with NAs)
sum(is.na(actiData))

#Devise a strategy for filling in all of the missing values in the dataset + Create a new dataset that is equal to the original dataset but with the missing data filled in
# the chosen strategy is simple. I am replacing the NA values with the mean steps value.

```{r}
meantot<- mean(actiData$steps, na.rm = T)
actiData$newSteps <- actiData$steps
actiData$newSteps[is.na(actiData$newSteps)]<- meantot
```
### 7. Histogram of the total number of steps taken each day after missing values are imputed
```{r}
tempoDat<- aggregate(steps ~ date, actiData, sum)
hist(tempoDat$steps)

```

### 8.Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends
```{r}
actiData<- mutate(actiData, Day = weekdays(actiData$date))
actiData<- mutate(actiData, weekend= ifelse(actiData$Day == c("Saturday", "Sunday"), "weekend", "week"))
tempoDat2 <- group_by(actiData, interval, weekend)
tempoDat2<- summarise(tempoDat2, mean(steps, na.rm = TRUE))
graph2<- ggplot(tempoDat2, aes(interval, `mean(steps, na.rm = TRUE)`, color = weekend))
graph2 + geom_bar(stat = "identity") + facet_grid(.~ tempoDat2$weekend)
```



